Ms 1

### 2017-08-14 ms1/ms1_display.Rmd
adjusted OR dx

>>>>

I also performed a similar analysis using logistic regression. I predicted whether a beneficiary would have a diagnosis at any point in the year. The main predictor variable was year, and the covariates were as elsewhere.

```{r adjusted_dx_or}
read_tsv('tables/model_dx.tsv') %>%
  filter(term=='year0') %>%
  model_ci() %>%
  select(diagnosis_type, change_str) %>%
  kable
```
